---
date: "09/14/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(include = TRUE)
carsdata <- mtcars
library(tidyverse)
library(magrittr)
library(knitr)
library(pander)
```

# Regression Models Course Project

## Assignment for the course project
You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions: <br>
- “Is an automatic or manual transmission better for MPG”  
- "Quantify the MPG difference between automatic and manual transmissions"  

## Executive Summary
The mtcars data set is a dataset included in R with 32 observations of 11 variables. These include MPG, Displacement, the vehicle's rear-axle ratio and 1/4 mile time. Using a simple linear regression that controls for size of engine (disp), size of car (drat), and relative acceleration (qsec), a manual transmission is usually better for a car's mileage than an automatic. On average, driving a vehicle with a manual transmission improves MPG by XXX.

## Descriptive Statistics  

```{r DescripStat, echo=FALSE}
"Summary of 'mpg' or Miles per Gallon"
temp <- summary(carsdata$mpg, carsdata$am)
pandoc.table(temp)
"Summary of 'disp' or Displacement(cu.in.) of engine"
temp <- summary(carsdata$disp)
pandoc.table(temp)
"Summary of 'drat' or the Rear-axle Ratio"
temp <- summary(carsdata$drat)
pandoc.table(temp)
"Summary of 'qsec' or the vehicle's 1/4 Mile Time"
temp <- summary(carsdata$qsec)
pandoc.table(temp)
```
### Descriptive Summary  

``` {r Plot 1 - MPG vs. Displacement, echo=FALSE}
carsdata %>% ggplot(aes(y = mpg, x = disp)) + 
             geom_line() + 
             labs(y = "MPG", 
                  x = "Engine Displacement (cu. in)", 
                  title = "Figure 1. MPG vs. Engine Displacement")
```

## Regression Analysis
```{r Specification 1 - Just Mileage, echo=FALSE}
model1 <- carsdata %>% lm(formula = mpg ~ am)
model2 <- carsdata %>% lm(formula = mpg ~ am + hp)
model3 <- carsdata %>% lm(formula = mpg ~ am + hp + wt)
model4 <- carsdata %>% lm(formula = mpg ~ am + wt + hp + drat)
mymodels <- list('Univariate on Automatic vs. Manual' = model1, 
                 'Bivariate on Automatic and Displacement' = model2, 
                  'As above but adds vehicle weight' = model3, 
                  'As above but adds Rear axle ratio' = model4)
lapply(mymodels, summary)
esti_func <- function(lm_model) {coef(summary(lm_model))["am", "Estimate"]}
pval_func <- function(lm_model) {coef(summary(lm_model))["am", "Pr(>|t|)"]}
am_estimates <- lapply(mymodels, esti_func)
am_pval <- lapply(mymodels, pval_func)
am_table <- map2_dfr(am_estimates, am_pval, ~ tibble(`Est.` = .x, `P.val` = .y))
am_table
```