---
date: "12/7/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = TRUE)
carsdata <- mtcars
library(tidyverse)
```

# Regression Models Course Project

## Assignment for the course project
You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions: <br>
- “Is an automatic or manual transmission better for MPG”  
- "Quantify the MPG difference between automatic and manual transmissions"  

## Executive Summary
The mtcars data set is a dataset included in R with 32 observations of 11 variables. These include MPG, Displacement, the vehicle's rear-axle ratio and 1/4 mile time. Using a simple linear regression that controls for size of engine (disp), size of car (drat), and relative acceleration (qsec), a manual transmission is usually better for a car's mileage than an automatic. On average, driving a vehicle with a manual transmission improves MPG by XXX.

## Descriptive Statistics
```{r cars, echo=FALSE}
print("Summary of 'mpg' or Miles per Gallon")
summary(carsdata$mpg)
print("Summary of 'disp' or Displacement(cu.in.) of engine")
summary(carsdata$disp)
print("Summary of 'drat' or the Rear-axle Ratio")
summary(carsdata$drat)
print("Summary of 'qsec' or the vehicle's 1/4 Mile Time")
summary(carsdata$qsec)
```
